---
title: "Weather Data Analysis"
author: "Sai Nanda Vihari"
date: "2025-02-18"
output: pdf_document
---

```{r setup, include=FALSE,warning=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Performing Weather Data Analysis on NYC Flights Departures using R


```{r}
# importing weather dataset using nycflights13 paackage
#import.packages("nycflights13")
library(nycflights13)
library(ggplot2)
head(weather)
# Getting Top 5 rows from the dataset
```
```{r}
#View column names
colnames(weather)
```

```{r}
#checking any null values are present or not
sum(is.na(weather))
```
```{r}
# removing these null values by omitting them
weather <- na.omit(weather)
```


## Univarient analysis

```{r}
# Summary statistics for Temperature

summary(weather$temp)

```

```{r}
# Summary statistics for Humidity

summary(weather$humid)

```



```{r}
hist(weather$temp, 
     main = "Histogram of Temperature", 
     xlab = "Temperature (F)", 
     col = "lightblue", 
     border = "black")
```

```{r}
# Using ggplot2, plotting the line plot of ‘temp’ as a function of ‘time_hour’
ggplot(weather, aes(x = time_hour, y = temp)) + geom_line(color = "steelblue") +
  labs(title = "NYC Departure Temperatures Over Time (2013)",
       x = "Time (hrs)",
       y = "Temp (F)")
```

```{r}
hist(weather$humid, 
     main = "Histogram of Humidity", 
     xlab = "Humidity (%)", 
     col = "lightgreen", 
     border = "black")
```


## Bivarient Analysis

```{r}
# Scatter plot of Temperature vs Dew Point 
plot(weather$temp, weather$dewp, 
     main = "Temperature vs. Dew Point",
     xlab = "Temperature (F)", 
     ylab = "Dew Point (F)", 
     col = "lightblue", 
     pch = 19)
```

```{r}
# Fit and add a regression line to the scatter plot
plot(weather$temp, weather$dewp, 
     main = "Temperature vs. Dew Point",
     xlab = "Temperature (F)", 
     ylab = "Dew Point (F)", 
     col = "lightblue", 
     pch = 19)
abline(lm(dewp ~ temp, data = weather), col = "red")
```

```{r}
# correlation between Temperature and Dew Point
correlation <- cor(weather$temp, weather$dewp, use = "complete.obs")
print(paste("Correlation between temperature and dew point:", round(correlation, 2)))
```


## Hypothesis Testing

***Null and Alternative Hypothesis: *** 

Null Hypothesis $H_0$: The true mean temperature of the dataset is 50°F.
Alternative Hypothesis $H_A$:  The true mean temperature of the dataset is not equal to 50°F.

***Normality Checking:***

```{r}
qqnorm(weather$temp, main = "QQ Plot of Temperature")
qqline(weather$temp, col = "red")
```
From the above Q-Q plot, we can say that most of the tail points are deviated from the line .So we are doing  shapiro Wiki Test for further checking normality.

```{r}
set.seed(17122000)
temp_sample <- sample(weather$temp, 500)
shapiro_test_result <- shapiro.test(temp_sample)
print(shapiro_test_result)
```
From the above test , P-value is greater than significant level $\alpha=0.05$ .So fail to reject null hypothesis . 
So Normality is approximately satisfied.

***Test Statistics:***

```{r}
t_test_result <- t.test(weather$temp, mu = 50)
print(t_test_result)
```

***Decision Making:***
From above Test Statistics ,  $P-Value=0.025$ is less than significant level $\alpha=0.05$ So Reject Null Hypothesis.

***Conclusion:***
We Can Conclude that The true mean temperature of the weather dataset is not equal to 50°F.





